%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Modified: Nathaniel Sawant
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Nathaniel Sawant} \\ \vspace{1pt}
  \small 609-433-8636 $|$ \href{mailto:sawant.na@northeastern.edu}{\underline{sawant.na@northeastern.edu}} $|$
  \href{https://swnt.io}{\underline{swnt.io}} $|$
  \href{https://linkedin.com/in/natesawant}{\underline{linkedin.com/in/natesawant}} $|$
  \href{https://github.com/natesawant}{\underline{github.com/natesawant}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Northeastern University, Khoury College of Computer Sciences}{Boston, MA}
{Bachelor of Science in Computer Science, Concentration in Artificial Intelligence}{Sep. 2021 -- May 2025}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
        \textbf{GPA}{: 3.69/4.00} \\
        \textbf{Leadership}{: Northeastern University IEEE Chapter (President, \emph{Fall 2023})} \\
        \textbf{Clubs}{: NUIEEE (Professional), NUHOC (Outdoors), NUPiC (Photography), Generate (Product Development)} \\
        \textbf{Relevant Courses}{: Database Management Systems, Machine Learning 1, Digital Design, Object-Oriented Design, Algorithms \& Data, Programming with C++, Artificial Intelligence, Probability \& Statistics} \\
        }}
\end{itemize}
\resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Go, Java, Python, C, C++, SQL (Oracle, SQLite), Java/TypeScript, HTML/CSS} \\
        \textbf{Frameworks}{: React, Tailwind, JUnit, FastAPI, Express} \\
        \textbf{Developer Tools}{: Git, Docker, AWS, GCP, NoSQL (MongoDB), VS Code, Visual Studio} \\
        \textbf{Libraries}{: OpenCV, pandas, NumPy, Matplotlib, Scikit-learn, Seaborn}
        }}
\end{itemize}


%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Software Engineer}{Jan. 2023 -- Jun. 2023}
{Fidelity Investments}{Boston, MA}
\resumeItemListStart
\resumeItem{Developed tool for rapid prototyping using company code with VSCode/Jupyter Lab integration.}
\resumeItem{Leveraged the ETL process to extract/save dozens of data points for 65,000 items from multiple sites.}
\resumeItem{Built Tableau dashboard to help visualize how 100+ databases are used when, how and by whom.}
\resumeItem{Integrated frontend with backend API powered by HuggingFace NLP transformer for $<$2 second searches.}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Oct. 2021 -- Aug. 2022}
{Rehabilitation Games \& Extended Reality Lab}{Boston, MA}
\resumeItemListStart
\resumeItem{Assisted in design of database for data collection of participants' eye-tracking captured at 100Hz.}
\resumeItem{Inplemented multiplayer gameplay mechanics using Unity 3D engine, OpenXR, and Photon Unity Networking.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR EXPERIENCE-----------
\resumeSubHeadingListStart

\section{Extracurricular Experience}
\resumeSubheading
{Software Engineer}{Sep. 2023 -- Present}
{Generate Product Development at Northeastern University}{Boston, MA}
\resumeItemListStart
\resumeItem{Designed REST APIs using MongoDB, Go, and the Echo web framework along with unit tests.}
\resumeItem{Implemented user registration frontend with React, React Hook Form, and Tailwind}
\resumeItem{Deployed microservice on AWS to estimate price of 3D print using modified open-source slicer.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Traffic Signal Detection} $|$ \emph{OpenCV, Python, C++}}{Nov. 2022}
\resumeItemListStart
\resumeItem{Trained Haar Cascade classifier to detect traffic signal and current color of the light.}
\resumeItem{Integrated computer vision model with simple robotic car to obey traffic signal rules.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Reinforcement Learning Agent} $|$ \emph{PyTorch, Unity, C\#}}{Mar. 2023}
\resumeItemListStart
\resumeItem{Trained and tested reinforcement learning agent that seeks target in unknown environment.}
\resumeItem{Integrated model with Unity for training and testing in virtual environment.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Brand Presence Tool} $|$ \emph{Azure Cognitive Services, OpenCV, Python, Git}}{Jul. 2022}
\resumeItemListStart
\resumeItem{Created analytics tool to detect brand presence in sponsored videos to measure brand metrics.}
\resumeItem{Developed as a prototype for Disrupt's Finnovate startup program, winning first place.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Image Manipulation Program} $|$ \emph{Java, Swing Framework, Git}}{Jun. 2022}
\resumeItemListStart
\resumeItem{Coded command line and graphical user interface for kernel-based image manipulation software.}
\resumeItem{Performed extensive testing with JUnit for validation/reliability and made Javadocs documentation.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}