%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Modified: Nathaniel Sawant
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Nathaniel Sawant} \\ \vspace{1pt}
  \small 609-433-8636 $|$ \href{mailto:sawant.na@northeastern.edu}{\underline{sawant.na@northeastern.edu}} $|$
  \href{https://linkedin.com/in/natesawant}{\underline{linkedin.com/in/natesawant}} $|$
  \href{https://github.com/natesawant}{\underline{github.com/natesawant}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Northeastern University}{Boston, MA}
{Bachelor of Science in Computer Science, Concentration in Artificial Intelligence}{Sep. 2021 -- May 2025}
\resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Go, Java, Python, C/C++, SQL (Oracle, SQLite), Java/TypeScript, HTML/CSS, R} \\
        \textbf{Frameworks}{: React, Node.js, JUnit, FastAPI, Express} \\
        \textbf{Developer Tools}{: Git, Docker, Amazon Web Services, Google Cloud Platform, VS Code, Visual Studio} \\
        \textbf{Libraries}{: pandas, NumPy, Matplotlib, OpenCV}
        }}
\end{itemize}


%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Software Data Engineer}{Jan. 2023 -- Jun. 2023}
{Fidelity Investments}{Boston, MA}
\resumeItemListStart
\resumeItem{Developed tool rapid prototyping with company code with VSCode/Jupyter Lab integration.}
\resumeItem{Interacted with FastAPI based backend that allowed for utilized natural language processing.}
\resumeItem{Utilized the ETL process to extract and save the price, quantity, etc., for ~65,000 products from multiple sites.}
\resumeItem{Created a Tableau dashboard to help visualize how 100+ databases are utilized who, when, and how.}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Oct. 2021 -- Aug. 2022}
{Rehabilitation Games \& Extended Reality Lab}{Boston, MA}
\resumeItemListStart
\resumeItem{Utilized Unity 3D engine, OpenXR, and Photon Unity Networking frameworks for development.}
\resumeItem{Designed backend system in C\# to synchronize both local and across network.}
\resumeItem{Assisted in development of eye-tracking data collection of participants in a database.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR EXPERIENCE-----------
\resumeSubHeadingListStart

\section{Extracurricular Experience}
\resumeSubheading
{Software Engineer}{Sep. 2023 -- Present}
{Generate Product Development at Northeastern University}{Boston, MA}
\resumeItemListStart
\resumeItem{Developed highly reusable React components for front-end made by design team.}
\resumeItem{Designed backend APIs using MongoDB, Go, and the Echo web framework.}
\resumeItemListEnd

\resumeSubheading
{Project Lead}{Oct. 2022 -- Mar. 2023}
{IEEE Micromouse Team at Northeastern University}{Boston, MA}
\resumeItemListStart
\resumeItem{Coordinated weekly meetings with five member team for a maze-solving robotics competition.}
\resumeItem{Distributed tasks to different team members with different timelines to meet the set deadlines.}
\resumeItem{Spearheaded the algorithms development of Arduino-based robot with sensor hardware in C/C++.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{URL Shortener} $|$ \emph{GCP, Express, MongoDB, Node.js, Javascript, HTML/CSS, Git}}{Aug. 2022}
\resumeItemListStart
\resumeItem{Designed and deployed a personal URL shortener on a Google Cloud Linux VM.}
\resumeItem{Used a Node.js backend with Express API to create and redirect the shortened URL.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Brand Presence Tools} $|$ \emph{Azure Cognitive Services, OpenCV, Python, Git}}{Jul. 2022}
\resumeItemListStart
\resumeItem{Created analytics tool to detect brand presence in sponsored videos to measure brand metrics.}
\resumeItem{Developed as a prototype for Disrupt's Finnovate startup program, winning first place.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Image Processing} $|$ \emph{Java, Swing Framework, Git}}{Jun. 2022}
\resumeItemListStart
\resumeItem{Designed command line and graphical user interface photo for basic manipulation software.}
\resumeItem{Performed extensive testing with JUnit for validation/reliability and used Javadocs documentation.}
\resumeItemListEnd
\resumeSubHeadingListEnd




%
%-----------OTHERS
\section{Activities}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Leadership}{: Northeastern University IEEE Chapter (President)} \\
        \textbf{Clubs}{: NUIEEE (Professional Organization), NUHOC (Outdoors Club), NUPiC (Photography Club), Generate} \\
        }}
\end{itemize}


%-------------------------------------------
\end{document}